Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex

    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\begin{tabular}{ccccccc}
	\toprule
	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\midrule
	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\

@@

	\end{tabular}
\end{table}

@@

\section{Conclusion}
To develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifers in this paper.
We formulate the choice of these classifiers into a search problem and design a heuristic search algorithm for it.
We implement this framework based on CDRP method for image classification task. 
In our experiment, we successfully reduce about $90\%$ computing consumption by pruning $90\%$ channels in the network while reach a high classification accuracy.

>>>>

    \caption{Encoding and Accuracy of Each Class Label}
    \label{tab:encoding-and-accuarcy}
	\scalebox{0.9}{
	\begin{tabular}{ccccccc}
	\toprule
	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
	\midrule
	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\

@@

	\end{tabular}
	}
\end{table}

@@

\section{Conclusion}
To develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifiers in this paper.
We formulate the problem of selecting and combining classifiers into a search problem and design a heuristic search algorithm to solve it.
We implement this framework based on CDRP method for image classification task. 
In our experiment, we successfully reduce about $90\%$ computing consumption by pruning $90\%$ channels in the network while reach a high classification accuracy.
